The Astropy Project:

### 2017-09-23 main.tex
adding section headings for APEs and concept of affiliated packages

\section{Major concepts}
% Anyone want to take this??

@@

@@

Astropy implements `normalized convolution' \citep[e.g.,][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.   In version $<=1.3$, the direct convolution and fft convolution approaches were not consistent, with fft convolution implementing normalized convolution and direct convolution implementing a different approach.  As of v2.0, the two methods are consistent and include a suite of consistency checks.

>>>>

\section{Major concepts}
% Anyone want to take this??
\subsection{APEs - Astropy Proposals for Enhancement}
% would be nice to write about the concept of APEs so we can refer to the
% relevant ones latr in the text

@@

\subsection{Concept of affiliated packages}
% it may be described in previous subsection, if not the Brigitta can try to
% write it up

@@

astropy implements `normalized convolution' \citep[e.g.,][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.   In version $<=1.3$, the direct convolution and fft convolution approaches were not consistent, with fft convolution implementing normalized convolution and direct convolution implementing a different approach.  As of v2.0, the two methods are consistent and include a suite of consistency checks.
